### 2021-04-22 paper/ase21/eval.tex
[ASE21] Applied more comments / Updated all numbers

      \myrowc
      {\mr{2}{\stextsf{\scriptsize Reference}}}
      {\me{2}{60}{125}{48.0}} {\me{2}{61}{98}{62.2}} {\me{2}{+1}{-27}{+14.2}}
      {\mr{1}{\stextsf{\scriptsize UnknownVar}}}
      {\me{1}{17}{81}{21.0}} {\me{1}{17}{53}{32.1}} {\me{1}{}{-28}{+11.1}}

      \myrowh
      {\mr{1}{\stextsf{\scriptsize DuplicatedVar}}}
      {\me{1}{43}{44}{97.7}} {\me{1}{44}{45}{97.8}} {\me{1}{+1}{+1}{+0.1}}

@@

      \smyrowc
      {\mr{1}{\stextsf{\scriptsize Assertion}}}
      {\mr{1}{\stextsf{\scriptsize Assertion}}}
      {\me{1}{5}{57}{8.8}} {\me{1}{5}{31}{16.1}} {\me{1}{}{-26}{+7.4}}

@@

      \mysrowh
      {\textbf{Total}}
      {91 / 299 (30.4\%)}{92 / 177 (52.0\%)}{+1 / -122 (+21.5\%)}

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/ttl-chro}
    \caption{TTLs sorted by creation time}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/ttl-count}
    \caption{The histogram of TTLs}
  \end{subfigure}
  \caption{Time to Lives (TTLs) of true bugs}
  \vspace*{-1.5em}
  \label{fig:ttl}
\end{figure}

@@

To understand the impact of the detected true bugs, we extended $\tool$ to
automatically extract when they are created and resolved in the ECMAScript
official repository.  A bug is \textit{created} when it exists
in a specific version but does not exist in its previous version, and
a bug is \textit{resolved} vice versa. The \textit{Time to Live (TTL)} of a bug denotes
the number of days between the created date and the resolved date.
Figure~\ref{fig:ttl} illustrates the TTLs of true bugs;
Figure~\ref{fig:ttl}(a) depicts the TTLs sorted by creation time and
Figure~\ref{fig:ttl}(b) depicts the histogram of the TTLs in a logarithmic scale.
Among \inred{93} true bugs, \inred{48} bugs are \textit{inherited},
which means that they are created before 2018,
and \inred{14} bugs still exist in the latest ECMAScript, which are newly detected by $\tool$.
We discuss the details of \inred{14} newly found bugs in Section~\ref{sec:new-bug}.
Even though we assume that \inred{48} inherited bugs are created on January 1, 2018,
the average TTL is \inred{414.5} and the maximum TTL is \inred{1,164}.
All the bugs with the maximum TTL are inherited ones and they are all newly detected.

@@

\begin{table*}
  \centering
  \caption{Type-related specification bugs newly detected by $\tool$ in the
  official draft of ECMAScript 2021 (ES12)}
  \label{table:new-bug}
  \resizebox{\textwidth}{!}{%
  \begin{tabular}{@{}c@{~}?c|@{~}c@{~}|l|c|@{~}c@{~}|@{~}r@{}}
    \multicolumn{1}{@{}c?}{\textbf{Name}} &
    \multicolumn{1}{c}{\textbf{Feature}} &
    \multicolumn{1}{@{}c@{~}}{\textbf{\#}} &
    \multicolumn{1}{c}{\textbf{Description}} &
    \multicolumn{1}{@{~}c@{~}}{\textbf{Checker}} &
    \multicolumn{1}{@{}c}{\textbf{Created}} &
    \multicolumn{1}{@{}c@{~}}{\textbf{TTL}}\\\specialrule{.1em}{.0em}{.0em}

@@

Among \inred{93} true bugs detected by $\tool$, \inred{14} are newly
detected and still exist in the latest version of ECMAScript.
Table~\ref{table:new-bug} summarizes the bugs, their
related JavaScript language features, and their TTLs.
Except for two bugs in ES12-8, all bugs were introduced in the initial
commit of the open development on September 22, 2015.
Thus, 12 newly detected bugs last for 1,996 days until March 9, 2021.
The two bugs in ES12-8 were created when a contributor introduced
the prefixes \textbf{?} and \textbf{!} on December 16, 2015, and they last for 1,910 days.
We reported the newly detected bugs to TC39, and all of them were
confirmed by the committee and will be fixed in ECMAScript 2022 (ES13).

>>>>

      \myrowc
      {\mr{2}{\stextsf{\scriptsize Reference}}}
      {\me{2}{62}{106}{58.5}} {\me{2}{63}{78}{80.8}} {\me{2}{+1}{-28}{+22.3}}
      {\mr{1}{\stextsf{\scriptsize UnknownVar}}}
      {\me{1}{17}{60}{28.3}} {\me{1}{17}{31}{54.8}} {\me{1}{}{-29}{+26.5}}

      \myrowh
      {\mr{1}{\stextsf{\scriptsize DuplicatedVar}}}
      {\me{1}{45}{46}{97.8}} {\me{1}{46}{47}{97.9}} {\me{1}{+1}{+1}{+0.1}}

@@

      \smyrowc
      {\mr{1}{\stextsf{\scriptsize Assertion}}}
      {\mr{1}{\stextsf{\scriptsize Assertion}}}
      {\me{1}{4}{56}{7.1}} {\me{1}{4}{31}{12.9}} {\me{1}{}{-25}{+5.8}}

@@

      \mysrowh
      {\textbf{Total}}
      {92 / 279 (33.0\%)}{93 / 157 (59.2\%)}{+1 / -122 (+26.3\%)}

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/life-sort}
    \caption{Life spans sorted by creation}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/life-hist}
    \caption{The histogram of life spans}
  \end{subfigure}
  \caption{Life spans of true bugs}
  \vspace*{-1.5em}
  \label{fig:life}
\end{figure}

@@

To understand the impact of the detected true bugs, we extended $\tool$ to
automatically extract when they are created and resolved in the ECMAScript
official repository.  A bug is \textit{created} when it exists
in a specific version but does not exist in its previous version, and
a bug is \textit{resolved} vice versa. The \textit{life span} of a bug denotes
the number of days between the created date and the resolved date.
Figure~\ref{fig:life} illustrates the life spans of true bugs;
Figure~\ref{fig:life}(a) depicts the life spans sorted by creation and
Figure~\ref{fig:life}(b) depicts the histogram of the life spans in a logarithmic scale.
Among \inred{93} true bugs, \inred{48} bugs are \textit{inherited},
which means that they are created before 2018,
and \inred{14} bugs still exist in the latest ECMAScript, which are newly detected by $\tool$.
We discuss the details of \inred{14} newly found bugs in Section~\ref{sec:new-bug}.
Even though we assume that \inred{48} inherited bugs are created on January 1, 2018,
the average life spans is \inred{414.5} and the maximum life span is \inred{1,164}.
All the bugs with the maximum life span are inherited ones and they are all newly detected.

@@

\begin{table*}
  \centering
  \caption{Type-related specification bugs newly detected by $\tool$ in the
  official draft of ECMAScript 2021 (ES12)}
  \label{table:new-bug}
  \resizebox{\textwidth}{!}{%
  \begin{tabular}{@{}c@{~}?c|@{~}c@{~}|l|c|@{~}c@{~}|@{~}r@{}}
    \multicolumn{1}{@{}c?}{\textbf{Name}} &
    \multicolumn{1}{c}{\textbf{Feature}} &
    \multicolumn{1}{@{}c@{~}}{\textbf{\#}} &
    \multicolumn{1}{c}{\textbf{Description}} &
    \multicolumn{1}{@{~}c@{~}}{\textbf{Checker}} &
    \multicolumn{1}{@{}c}{\textbf{Created}} &
    \multicolumn{1}{@{}c@{~}}{\textbf{Life Span}}\\\specialrule{.1em}{.0em}{.0em}

@@

Among \inred{93} true bugs detected by $\tool$, \inred{14} are newly
detected and still exist in the latest version of ECMAScript.
Table~\ref{table:new-bug} summarizes the bugs, their
related JavaScript language features, and their life spans.
Except for two bugs in ES12-8, all bugs were introduced in the initial
commit of the open development on September 22, 2015.
Thus, 12 newly detected bugs last for 1,996 days until March 9, 2021.
The two bugs in ES12-8 were created when a contributor introduced
the prefixes \textbf{?} and \textbf{!} on December 16, 2015, and they last for 1,910 days.
We reported the newly detected bugs to TC39, and all of them were
confirmed by the committee and will be fixed in ECMAScript 2022 (ES13).
